\documentclass[a4paper]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{cascadia-code}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection {K,}{Ankesh \fontsize{20}{15}\selectfont [Sr. DevOps Engineer]}{{\urlstyle{same}\href{www.ankesh.co.in}{www.ankesh.co.in}}\\
\href{mailto:iankesh@outlook.com}{iankesh@outlook.com} | \href{tel: +918197434654}{+91 819.743.4654}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University - \href{https://www.ljmu.ac.uk/}{L.J.M.U.}}
\descript{M.S. [Masters of Science]}
\location{2022 - 2024 | Liverpool, UK}
Liverpool John Moores University \\
\sectionsep

\subsection{University - \href{https://vtu.ac.in/en/}{V.T.U.}}
\descript{B.E. [Bachelor of Engineering]}
\location{2011 - 2015 | Bengaluru, IN}
AMC Engineering College \\
%\sectionsep

% \subsection{C.B.S.E.}
% \descript{H.Sc. in Science}
% \location{2008-2010 | Ranchi, IN}
% D.A.V. Public School \\
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links} 
Github:// \href{https://github.com/iankesh}{\bf iAnkesh} \\
LinkedIn://  \href{https://www.linkedin.com/in/iankesh}{\bf iAnkesh} \\
YouTube://  \href{https://www.youtube.com/c/iAnkesh}{\bf iAnkesh} \\
% Quora://  \href{https://www.quora.com/iankesh}{\bf iAnkesh} \\
Blogs://  \href{https://iankesh.blogspot.com/2020/08/my-blogs.html}{\bf iAnkesh} \\
% Twitter://  \href{https://twitter.com/thisisankesh}{\bf @thisisAnkesh}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Python \textbullet{}  Shell \textbullet{} KQL \textbullet{} PowerShell 
 \textbullet{} Java \textbullet{} Groovy \textbullet{} YAML \textbullet{} \LaTeX \\ 
 \sectionsep
\subsection{DevOps}
\location{CI / CD:}
Jenkins \& GitLab - Pipeline as Code \textbullet{} Bamboo \textbullet{} Azure DevOps \textbullet{} Rundeck \textbullet{} Gunicorn \textbullet{} Teamcity \\
\location{Configuration Management:} 
Terraform \textbullet{} Scalr \textbullet{} Ansible \textbullet{} Chef Basics \\
\location{Cloud Operations:} 
Azure \textbullet{} AWS \textbullet{} Oracle Cloud \\
\location{Containerization:} 
Docker \textbullet{} Kubernetes \textbullet{} Podman \\
\location{Security / Code Quality:} 
SonarQube \textbullet{} Checkov \textbullet{} Prisma Cloud \\
\location{Build \& Repo Mgmt.:} 
Packer \textbullet{} Maven \textbullet{} JFrog Artifactory \\
\location{Web Tools \& Technologies:} 
Apache Tomcat \textbullet{} Nginx \textbullet{} HA Proxy \\
\location{Monitoring / Logging:} 
Grafana \textbullet{} Nagios \textbullet{} Log Analytics \\
\location{Version Control:} 
Git \textbullet{} GitHub \textbullet{} GitLab \textbullet{} Bitbucket \\
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Volunteering
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Volunteering}
\subsection{Professional}
Tech Bites - Speaker \\
Danaher Newsletter - Article Writer \\
Fundo Club - Founder \\
\sectionsep

\subsection{Academics}
Event Organiser \\
Graphics Designer

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Professional Journey |  \bf\fontsize{10}{15}\selectfont Total - 7+ Years}
\href{https://www.goldmansachs.com/}{\runsubsection{Goldman Sachs}}
\descript{| Senior Associate - DevOps }
\location{2021 Sep - Present | Bengaluru, IN}
\sectionsep
\href{https://www.danaher.com/}{\runsubsection{Danaher Corporation}}
\descript{| SDE II - DevOps }
\location{2019 Apr – 2021 Sep | Bengaluru, IN}
\sectionsep
\href{https://www.ltimindtree.com/}{\runsubsection{LTI Mindtree}}
\descript{| Software Engineer - DevOps }
\location{2016 Feb – 2019 Apr | Chennai, IN}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize} %\fontsize{11.5}{0}\selectfont
\item Architecting Azure/OCI/AWS cloud infrastructure by writing IaC Terraform configuration and developing Terraform modules.
\item Developing programs for multiple data analysis and creating/deploying frontends using Python, Gunicorn, Flask and Nginx.
\item Setting up GitLab runners on the servers hosted on Data-Center to run the data pipeline which pulls data the on-premise datasources to reduce the data transfer time to approx. 50\% .
\item Architected and created environments for a product called \href{https://www.hach.com/claros/overview#claros-video}{\bf Claros} across multiple regions using IaC and written custom Ansible roles, which helped reduce the per deployment time by 2 hrs.
\item Created multiple custom docker images and pushed them to GitLab private registries to be used to create GitLab runner containers while running a job.
\item Implemented a conduit based project which pushes the code artifact to GNS and then pull it to the on-premise DC hosts for deployment.
\item Developed an E2E Monitoring Solution using Grafana and Nagios which reduced prod incidents from 50+/quarter to <10/quarter.
\item Designed a cost-effective build system and improved the efficiency by 80\% using Azure Kubernetes build agents and on-demand Docker containers.
\item Implemented security standards by using SonarQube and Checkov which increased the code quality by 50\% for application and 30\% for infrastructure.
\item Saved approx. US\$ 2 Million by performing resource optimization on cloud using Kusto Query language - KQL, Log Analytics and Application Insights and also set-up cost metrics and alerts.
\item Designed the E2E Build and Release process for a tenant based multiservice architecture and achieved the prod release success rate of 100\%.
\item Developed a company proprietary tool named \href{https://www.youtube.com/watch?v=YWLU2OU13tA}{\bf D-Engine}, and it is used for infrastructure orchestration across the organization.
\item Automated Cloud (AWS \& Azure) infrastructure provisioning using Terraform, Packer and Ansible.
\item Setup Application proxy to be used from instances by writing proxy rules and deploying then to sky-connect for connecting on-premise services to outside services like detectify, snowflake hosted on AWS cloud, etc.
\item Automated the repetitive operational tasks and reduced the MTTR by 95\%.
\item Worked closely with Dev, QA and Firmware teams to understand the release scope and maintain the infrastructure state.
\item Incorporating DevOps and Scrum best practices across the teams.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Interest and Hobbies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests \& Hobbies}
\descript{Interests}
Blogging \textbullet{} Designing \textbullet{} Volunteering \textbullet{} Trading \& Finance \\
\descript{Hobbies}
Running \textbullet{} Fitness \textbullet{} Cooking \textbullet{} Reading  \textbullet{} Listening to Music


\end{minipage} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hfill
% \begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\topsep}
\vspace{\topsep}
\vspace{\topsep}
\vspace{\topsep}
\section{Total Experience |  \bf\fontsize{10}{15}\selectfont Total - 7+ Years}
\runsubsection{Goldman Sachs}
\descript{| Senior Associate - DevOps }
\location{Sep 2021 - Present | Bengaluru, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Setting up Data pipelines for multiple data analysis stages like ingest, model, program and outbound.
\item Developed the complete backend for Digital Risk Operations (DRO) framework which was multi environment data modelling and alalytics platform.
\item Migrating Product Risk Analytics On-premise tools to AWS cloud by writing IaC Terraform configuration and developing Terraform modules.
\item Setting up GitLab pipelines for frontend/infra projects.
\item Developing Python programs for multiple data analysis and creating/deploying frontends using Python, Gunicorn, Flask and Nginx.
\item Designing Container based solution for multi-env data analytics.
\item Setup the complete Atlassian suite for the team with all the dashboards, sprint boards, epics in Jira, created confluence space for the team ans integrated both with the CI platform.
\item Incorporating DevOps and Scrum best practices across the teams.
\end{tightemize}
\sectionsep

\runsubsection{Danaher Corporation}
\descript{| SDE II - DevOps }
\location{Apr 2019 – Sep 2021 | Bengaluru, IN}
\begin{tightemize}
\item Architected and created environments for a product called \href{https://www.hach.com/claros/overview#claros-video}{\bf Claros} across multiple regions using IaC - Terraform and written custom Ansible roles, which helped reduce the per deployment time by 2 hrs.
\item Developed an E2E Monitoring Solution using Grafana and Nagios which reduced prod incidents from 50+/quarter to <10/quarter.
\item Designed a cost-effective build system and improved the efficiency by 80\% using Azure Kubernetes build agents and on-demand Docker containers.
\item Implemented security standards by using SonarQube and Checkov which increased the code quality by 50\% for application and 30\% for infrastructure.
\item Saved approx. US\$ 2 Million by performing resource optimization on cloud using Kusto Query language - KQL, Log Analytics and Application Insights and also set-up cost metrics and alerts.
\item Streamlining release process by automating deployments at multiple stages.
\end{tightemize}
\sectionsep

\runsubsection{Mindtree}
\descript{| Software Engineer - DevOps }
\location{Feb 2016 – Apr 2019 | Chennai, IN}
\begin{tightemize}
\item Designed the E2E Build and Release process for a tenant based multiservice architecture and achieved the release success rate of 100\%.
\item Developed a company proprietary tool named \href{https://www.youtube.com/watch?v=YWLU2OU13tA}{\bf D-Engine}, and it is used for infrastructure orchestration across the organization.
\item Created a visual dashboard using Grafana and Prometheus to display the response from 32k+ stores across the country.
\item Automated Cloud (AWS \& Azure) infrastructure provisioning using Terraform, Packer and Ansible.
\item Automated the repetitive operational tasks and reduced the MTTR by 95\%.
\item Worked closely with Dev, QA and Firmware teams to understand the release scope and maintain the infrastructure state.
\end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\vspace{\topsep}
\begin{tightemize}
\item Cloud Computing with AWS \\
\item Jenkins Professional \\
\item Docker for DevOps \\
\item DBS Problem Solving Practice \\
\item Microsoft Azure Administrator \\
\item Situational Self Leadership
\end{tightemize}
\sectionsep

% \end{minipage} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}\
2021	 & Received & Above \& Beyond Award \\
2020	 & Received & Global ACE Award \\
2020	 & Nominated& GEM Award\\
2019     & Received & PILLAR Award \\
2018     & Received & Outstanding Performer Award  \\
2017     & Won      & Osmosis \\
2016     & Received & Spot Award
\end{tabular}
\sectionsep

\end{document}  \documentclass[]{article}

